---
title: "Maternal transfer of per- and polyfluoroalkyl substances (PFAS) in wild birds: a systematic review and meta-analysis"
subtitle: "Supplementary Information - Model outputs"
author: "Anonymous author"
date: "2024-02-19"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    toc_depth: 2
    number_sections: no
    theme: cerulean
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, echo=FALSE, message=FALSE}
options(repr.matrix.max.cols=Inf, repr.matrix.max.rows=Inf)
knitr::opts_chunk$set(
  message = FALSE, #turning off the display of messages
  warning = FALSE,#turning off the display of warnings
  tidy = TRUE, #turning on the "tidy" option (which affects the formatting of code chunks)
  cache = TRUE, #turning on caching (so that code chunks are only executed if their dependencies have changed)
  echo = TRUE #turning on the "echo" option (so that code is displayed in the output)
)

rm(list = ls()) #Effectively clears the environment of any data, functions, or variables that have been defined

# using the pacman package to load multiple packages at once
pacman::p_load(tidyverse, #a collection of packages for data manipulation, visualization, and modeling, including packages like dplyr, ggplot2, and tidyr
               readr, #a package for reading and writing tabular data, such as CSV files
               here, #a package for working with file paths, particularly when working with project-based workflows
               dplyr, #a package for data manipulation, which is already included in the tidyverse package
               metafor, #a package for conducting meta-analyses
               meta, #a package for conducting meta-analyses
               orchaRd, #a package for working with ordination data
               kableExtra, #a package for creating tables and formatting them in R Markdown documents
               patchwork, #a package for combining multiple plots into a single figure
               MuMIn, #a package for model selection and multimodel inference,
               ape,
               formatR,
               curl,
               rotl,
               clubSandwich
               )
dat <- read_csv(here("RData", "dat.csv"), show_col_types = FALSE)
```

# Phylogenetic tree
For more information on the construction of the tree, see file "tree_MA_MT_PFAS.Rmd".

```{r, load the tree}
tree <- read.tree(here("R", "phylogenetic_tree.tre")) #check tree_MA_MT_PFAS.Rmd for tree construction
tree$tip.label <- gsub("_"," ", tree$tip.label) #get rid of the underscores
tree$node.label <- NULL #deleting internal node labels

plot(tree, cex=1.1, label.offset =.1, no.margin = TRUE)
#or plot to pdf
# pdf("figs/phylogenetic_tree.pdf", width=8, heigh=16)
# plot(tree, cex=1.5, label.offset =.1, no.margin = TRUE)
#dev.off()
```

# Intercept meta-analytic models

## Model 1: Overall meta-analytic model

```{r, eval=FALSE}
ma_model <- rma.mv(yi = lnRR,
             V = VCV_lnRR, 
             random = list(~1|study_ID,
                           ~1|pfas_ID,
                           ~1|es_ID
              ),
             test = "t",
             data = dat)
ma_model_rob <- robust(ma_model, dat$measurement_ID_P)
```

```{r}
load(here("RData", "ma_model.RData"))
summary(ma_model)
i2_ml(ma_model)
```

```{r}
I2 <- orchaRd::i2_ml(ma_model)
orchaRd::orchard_plot(ma_model,
             mod = "1",
             group = "study_ID", 
             xlab = "lnRR",
             alpha = 0.6,
             trunk.size = 3,
             branch.size = 1.5,
             twig.size = 1,
             k.pos = "right",
             colour = TRUE,
             fill = FALSE) +  
  annotate(geom = "text",
           x = 1.2,
           y = 6.2, 
           label = paste0("italic(I)^{2} == ", round(I2[1],4)),
           color ="black",
           parse = TRUE, 
           size = 3.5) +
           #scale_colour_manual(values = "darkorange")+ # change colours
           #scale_fill_manual(values="darkorange")+ 
           scale_size_continuous(range = c(1, 7)) + # change point scaling
  ggtitle("") +
  theme(panel.border = element_rect(colour = "black", 
                                             fill=NA,
                                             size=1.3), # border around the plot
                 text = element_text(size = 15), # change font sizes
                 legend.title = element_text(size = 12),
                 legend.text = element_text(size = 10)) +
  xlab("Intercept")
```

## Model 2: Meta-analytic model with all random effects

```{r, eval=FALSE}
ma_all_random_effects <- rma.mv(yi = lnRR,
                                V = VCV_lnRR, # Add `VCV_lnRR` to account for correlated errors
             random = list(~1|study_ID, # Between-study effect
                           ~1|Phylogeny, # Phylogenetic correlation between species
                           ~1|species_ID, # Between species effect
                           ~1|pfas_ID, # Between type of PFAS effect
                           ~1|es_ID # Within-study effect
              ),
             R = list(Phylogeny = cor_tree),
             test = "t",
             data = dat)
ma_all_random_effects <- robust(ma_all_random_effects, dat$measurement_ID_P)
```

```{r}
load(here("RData", "ma_all_random_effects.RData"))
summary(ma_all_random_effects)
i2_ml(ma_all_random_effects)
```

## Model 3: Meta-analytic model without albumen data

```{r, eval=FALSE}
ma_model_no_albumen <- rma.mv(yi = lnRR,
             V = VCV_lnRR_no_albumen, 
             random = list(~1|study_ID,
                           ~1|pfas_ID,
                           ~1|es_ID
              ),
             test = "t",
             data = dat_no_albumen)

ma_model_no_albumen <- robust(ma_model_no_albumen, dat_no_albumen$measurement_ID_P)
```

```{r}
load(here("RData", "ma_model_no_albumen.RData"))
summary(ma_model_no_albumen)
i2_ml(ma_model_no_albumen)
```

```{r}
I2_no_albumen <- orchaRd::i2_ml(ma_model_no_albumen)
orchaRd::orchard_plot(ma_model_no_albumen,
             mod = "1",
             group = "study_ID", 
             xlab = "lnRR",
             alpha = 0.6,
             trunk.size = 3,
             branch.size = 1.5,
             twig.size = 1,
             k.pos = "right",
             colour = TRUE,
             fill = FALSE) +  
  annotate(geom = "text",
           x = 1.2,
           y = 6.2, 
           label = paste0("italic(I)^{2} == ", round(I2_no_albumen[1],4)),
           color ="black",
           parse = TRUE, 
           size = 3.5) +
           #scale_colour_manual(values = "darkorange")+ # change colours
           #scale_fill_manual(values="darkorange")+ 
           scale_size_continuous(range = c(1, 7)) + # change point scaling
           theme(panel.border = element_rect(colour = "black", 
                                             fill=NA,
                                             size=1.3), # border around the plot
                 text = element_text(size = 18), # change font sizes
                 legend.title = element_text(size = 15),
                 legend.text = element_text(size = 13)) +
  xlab("Intercept")

```

# Model runnig function
The following function was used to run meta-regression analysis
```{r}
run_model <- function(data, formula){
  data <- as.data.frame(data) # convert data set into a data frame to calculate VCV matrix 
  VCV <- impute_covariance_matrix(data$var_lnRR,
                                     cluster = data$measurement_ID_A,
                                     r = 0.5) # create VCV matrix for the specified data
  rma.mv(lnRR,
         var_lnRR, # run the model, as described earlier
         mods = formula,
         random = list(~1|study_ID,
                       ~1|pfas_ID,
                       ~1|es_ID),
         test = "t",
         data = data,
         sparse = TRUE)
}
```

# Single-moderator metaregression models

## Model 4: Carbon chain length

```{r}
sum(is.na(dat$carbon_chain_length)) #checking the amount of NAs
#[1] 65
dat_ccl <- dat[complete.cases(dat[ , "carbon_chain_length"]),]
sum(is.na(dat_ccl$carbon_chain_length))
#[1] 0
```

```{r}
ccl_model <- run_model(dat_ccl, ~scale(carbon_chain_length))
ccl_model <- robust(ccl_model, dat_ccl$measurement_ID_P)
save(ccl_model, file = here("Rdata", "ccl_model.RData"))
```

```{r}
load(here("RData", "ccl_model.RData"))
summary(ccl_model)
r2_ml(ccl_model, dat_ccl)
```

```{r}
r2_ccl <- r2_ml(ccl_model, dat_ccl)
ccl_bubble <- orchaRd::mod_results(ccl_model, 
                                   mod = "carbon_chain_length", 
                                   group = "study_ID")
                                   
  
bubble_plot(ccl_bubble,
            mod = "carbon_chain_length",
            group = "study_ID",
            x = "carbon_chain_length",
            y = "lnRR",
            est.lwd = 1,
            legend.pos = "bottom.right",
            k.pos = "bottom.left",
            ci.col = "red",
            pi.col = "black",
            est.col = "black",
            g = TRUE) +
  annotate(geom ="text",
           x = 7,
           y = 6.2,
           label = paste0("italic(R)^{2} == ", round(r2_ccl[1],4)),
           color = "black",
           parse = TRUE,
           size = 4) +
  ggtitle("") +
  theme(plot.title = element_text(size = 18),
        legend.position = "none",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 14)) +
  xlab("Carbon chain length")
```

## Model 5: Molecular weight

```{r, eval=FALSE}
mw_model <- run_model(dat, ~scale(molecular_weight))
mw_model <- robust(mw_model, dat$measurement_ID_P)
```

```{r}
load(here("RData", "mw_model.RData"))
summary(mw_model)
r2_ml(mw_model, dat)
```

```{r}
r2_mw <- r2_ml(mw_model, dat)

mw_bubble <- orchaRd::mod_results(mw_model,
                          mod = "molecular_weight",
                          group = "study_ID")

orchaRd::bubble_plot(mw_bubble, 
            mod = "molecular_weight", 
            group = "study_ID",
            xlab = "molecular_weight",
            ylab = "lnRR",
            legend.pos = "bottom.right",
            k.pos = "bottom.left",
            ci.col = "red",
            pi.col = "black",
            g = TRUE) +
  annotate(geom ="text",
           x= 350,
           y= 6, 
           label= paste0("italic(R)^{2} == ", round(r2_mw[1],4)),
           color="black",
           parse = TRUE, 
           size = 4) +
  ggtitle("") +
  theme(plot.title = element_text(size = 18),
        legend.position = "none",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 14)) +
  xlab("Molecular weight")
```

## Model 6: Functional group

```{r, eval=FALSE}
fun_gro_model <- run_model(dat_fg, ~ functional_group - 1)
fun_gro_model <- robust(fun_gro_model, dat_fg$measurement_ID_P)
```

```{r}
load(here("RData", "fun_gro_model.RData"))
summary(fun_gro_model)
r2_ml(fun_gro_model, dat_fg)
```

```{r}
r2_fun_gro <- r2_ml(fun_gro_model, dat_fg)

orchard_plot(fun_gro_model,
             mod = "functional_group",
             group = "study_ID",
             xlab = "lnRR",
             legend.pos = "bottom.right",
             k.pos = "right",
             angle = 90,
             colour = "black",
             fill = FALSE,
             trunk.size = 5,
             branch.size = 1.1,
             twig.size = 0.5) +
  annotate(geom = "text",
           x = 4.4,
           y = -6, 
           label = paste0("italic(R)^{2} == ", round(r2_fun_gro[1],4)),
           color ="black",
           parse = TRUE, 
           size = 4) +
  ggtitle("")+
  theme(plot.title = element_text(size = 18),
        legend.position = "none",
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text.y = element_text(size = 14),
       axis.text.x = element_text(size = 14))
```

## Model 7: Clutch size

```{r, eval=FALSE}
sum(is.na(dat$clutch_size))
#[1] 0
clutch_size_model <- run_model(dat, ~ clutch_size)
```

```{r}
load(here("RData", "clutch_size_model.RData"))
summary(clutch_size_model)
r2_ml(clutch_size_model, dat)
```

```{r}
r2_clutch <- r2_ml(clutch_size_model, dat)

bubble_plot(clutch_size_model,
             mod = "clutch_size",
             group = "study_ID", 
             xlab = "clutch_size",
             ylab = "lnRR",
             legend.pos = "bottom.right",
             k.pos = "top.right",
             ci.col = "red",
             pi.col = "black",
             g = TRUE) +
  annotate(geom = "text",
           x = 1.5,
           y = -7, 
           label = paste0("italic(R)^{2} == ", round(r2_clutch[1],4)),
           color = "black",
           parse = TRUE, 
           size = 4) +
  ggtitle("") +
  theme(plot.title = element_text(size = 19),
        legend.position = "none",
        axis.title.x = element_text(size = 17),
        axis.title.y = element_text(size = 17),
        axis.text = element_text(size = 15)) +
  xlab("Clutch size")
```

## Model 8: Egg weight

```{r, echo=FALSE}
sum(is.na(dat$egg_weight_mean))
#[1] 67
dat_egg_weight <- dat[complete.cases(dat[ , "egg_weight_mean"]),] #removing NAs
sum(is.na(dat_egg_weight$egg_weight_mean))
#[1] 0
```

```{r, eval=FALSE}
egg_weight_model <- run_model(dat_egg_weight, ~ egg_weight_mean)
```

```{r}
load(here("RData", "egg_weight_model.RData"))
summary(egg_weight_model)
r2_ml(egg_weight_model, dat_egg_weight)
```

```{r}
r2_egg_weight <- r2_ml(egg_weight_model, dat_egg_weight)

bubble_plot(egg_weight_model,
             mod = "egg_weight_mean",
             group = "study_ID",
             xlab = "egg_weight_mean",
             ylab = "lnRR",
             legend.pos = "bottom.right",
             k.pos = "top.right",
             ci.col = "red",
             pi.col = "black",
             g = TRUE) +
  annotate(geom = "text",
           x = 20,
           y = -6.7, 
           label = paste0("italic(R)^{2} == ", round(r2_egg_weight[1],4)),
           color = "black",
           parse = TRUE, 
           size = 4) +
  ggtitle("") +
  theme(plot.title = element_text(size = 19),
        legend.position = "none",
        axis.title.x = element_text(size = 17),
        axis.title.y = element_text(size = 17),
        axis.text = element_text(size = 15)) +
  xlab("Egg weight")
```

## Model 9: Body weight

```{r, eval=FALSE}
sum(is.na(dat$body_weight_mean))
#[1] 0
body_weight_model <- run_model(dat, ~ body_weight_mean)
```

```{r}
load(here("RData", "body_weight_model.RData"))
summary(body_weight_model)
r2_ml(body_weight_model, dat)
```

```{r}
r2_body_weight <- r2_ml(body_weight_model, dat)

bubble_plot(body_weight_model,
             mod = "body_weight_mean",
             group = "study_ID",
             xlab = "body_weight_mean",
             ylab = "lnRR",
             legend.pos = "bottom.right",
             k.pos = "top.right",
             ci.col = "red",
             pi.col = "black",
             g = TRUE) +
  annotate(geom = "text",
           x = 400,
           y = -7, 
           label= paste0("italic(R)^{2} == ", round(r2_body_weight[1],4)),
           color="black",
           parse = TRUE, 
           size = 4) +
  ggtitle("") +
  theme(plot.title = element_text(size = 19),
        legend.position = "none",
        axis.title.x = element_text(size = 17),
        axis.title.y = element_text(size = 17),
        axis.text = element_text(size = 15)) +
  xlab("Body weight")
```

## Model 10: Laying order

```{r, eval=FALSE}
sum(is.na(dat$laying_order))
#[1] 315
laying_order_model <- run_model(dat, ~scale(laying_order))
```

```{r}
load(here("RData", "laying_order_model.RData"))
summary(laying_order_model)
r2_ml(laying_order_model, dat)
```

```{r}
r2_laying_order <- r2_ml(laying_order_model, dat)
bubble_plot(laying_order_model,
             mod = "laying_order",
             group = "study_ID",
             xlab = "laying_order",
             ylab = "lnRR",
             legend.pos = "bottom.right",
             k.pos = "top.right",
             ci.col = "red",
             pi.col = "black",
             g = TRUE) +
  annotate(geom = "text",
           x = 1.15,
           y = -3, 
           label= paste0("italic(R)^{2} == ", round(r2_laying_order[1],4)),
           color="black",
           parse = TRUE, 
           size = 4) +
  ggtitle("") +
  theme(plot.title = element_text(size = 19),
        legend.position = "none",
        axis.title.x = element_text(size = 17),
        axis.title.y = element_text(size = 17),
        axis.text = element_text(size = 15)) +
  xlab("Laying order")
```

## Model 11: Sample type - adult

```{r, eval=FALSE}
sample_type_a_model <- run_model(dat, ~ sample_type_A - 1)

sample_type_a_model <- robust(sample_type_a_model, dat$measurement_ID_P)
```

```{r}
load(here("RData", "sample_type_a_model.RData"))
summary(sample_type_a_model)
r2_ml(sample_type_a_model, dat)
```

```{r}
r2_sample_type_a <-  r2_ml(sample_type_a_model, dat)

orchard_plot(sample_type_a_model,
             mod = "sample_type_A",
             group = "study_ID", 
             xlab = "lnRR",
             k.pos = "left",
             angle = 45,
             colour = FALSE,
             fill = FALSE,
             trunk.size = 4,
             branch.size = 1,
             twig.size = 0.5
             ) +
  annotate(geom="text",
           x= 9.4,
           y= 5, 
           label= paste0("italic(R)^{2} == ", round(r2_sample_type_a[1],4)),
           color="black",
           parse = TRUE, 
           size = 3) +
  ggtitle("") +
  theme(plot.title = element_text(size = 16),
        legend.position = "none",
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text.y = element_text(size = 12),
       axis.text.x = element_text(size = 12))
```

## Model 12: Sample type - progeny

```{r, eval=FALSE}
sample_type_p_model <- run_model(dat, ~ sample_type_P - 1)

sample_type_p_model <- robust(sample_type_p_model, dat$measurement_ID_P)
```

```{r}
load(here("RData", "sample_type_p_model.RData"))
summary(sample_type_p_model)
r2_ml(sample_type_p_model, dat)
```

```{r}
r2_sample_type_p <-  r2_ml(sample_type_p_model, dat)

orchard_plot(sample_type_p_model,
             mod = "sample_type_P",
             group = "study_ID", 
             xlab = "lnRR",
             k.pos = "left",
             angle = 45,
             colour = FALSE,
             fill = FALSE,
             trunk.size = 4,
             branch.size = 1,
             twig.size = 0.5
             ) +
  annotate(geom="text",
           x= 5.4,
           y= 5, 
           label= paste0("italic(R)^{2} == ", round(r2_sample_type_p[1],4)),
           color="black",
           parse = TRUE, 
           size = 3) +
  ggtitle("b)") +
  theme(plot.title = element_text(size = 16),
        legend.position = "none",
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text.y = element_text(size = 12),
       axis.text.x = element_text(size = 12))
```

## Model 13: Bird's diet

```{r, echo=FALSE}
sum(is.na(dat$diet))
#[1] 0

dat_diet <- dat %>%
  mutate(diet = case_when(
    diet == "Piscivorous, avivorous and kleptoparasite" ~ "Diet type 1",
    diet == "Piscivorous" ~ "Diet type 2",
    diet == "Opportunistic and diverse" ~ "Diet type 3",
    diet == "Omnivorous" ~ "Diet type 4",
    diet == "Insectivorous" ~ "Diet type 5",
    TRUE ~ diet
  ))
```

```{r, eval=FALSE}
diet_model <- run_model(dat_diet, ~ diet - 1)

diet_model <- robust(diet_model, dat_diet$measurement_ID_P)
summary(diet_model)
```

```{r}
load(here("RData", "diet_model.RData"))
summary(diet_model)
r2_ml(diet_model, dat_diet)
```

```{r}
r2_diet <- r2_ml(diet_model, dat_diet)

orchard_plot(diet_model,
             mod = "diet",
             group = "study_ID",
             xlab = "lnRR",
             k.pos = "left",
             angle = 45,
             colour = FALSE,
             fill = FALSE,
             trunk.size = 4,
             branch.size = 1,
             twig.size = 0.5
             ) +
  annotate(geom="text",
           x = 5.4,
           y = 5, 
           label= paste0("italic(R)^{2} == ", round(r2_diet[1],4)),
           color="black",
           parse = TRUE, 
           size = 3) +
  ggtitle("c)") +
  theme(plot.title = element_text(size = 16),
        legend.position = "none",
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text.y = element_text(size = 12),
       axis.text.x = element_text(size = 12))
```

## Model 14: Life stage progeny (i.e., egg OR chick)

```{r, eval=FALSE}
sum(is.na(dat$life_stage_P))
#[1] 0
life_stage_model <- run_model(dat, ~ life_stage_P - 1)

life_stage_model <- robust(life_stage_model, dat$measurement_ID_P)
```

```{r}
load(here("RData", "life_stage_model.RData"))
summary(life_stage_model)
r2_ml(life_stage_model, dat)
   # R2_marginal R2_conditional 
   #  0.00278897     0.07829010 

fig_life_stage_p <- orchard_plot(life_stage_model,
             mod = "life_stage_P",
             group = "study_ID",
             xlab = "lnRR",
             angle = 45,
             colour = FALSE,
             fill = FALSE,
             trunk.size = 2,
             branch.size = 1,
             twig.size = 0.5) +
  ggtitle("") +
  theme(plot.title = element_text(face = "bold"))

fig_life_stage_p
```

# Multi-moderator Model

## Model 15: Full model

```{r, eval=FALSE}
full_model1 <- rma.mv(yi = lnRR,
                      V = VCV_lnRR2, 
                      mods = ~  1 + 
                        functional_group +
                        scale(carbon_chain_length) +
                        sample_type_A +
                        sample_type_P +
                        scale(clutch_size) +
                        scale(body_weight_mean) +
                        scale(egg_weight_mean) +
                        diet,
                        #life_stage_P,
                      random = list(~1|study_ID,
                                    ~1|pfas_ID, 
                                    ~1|es_ID
                                    ),
                      method = "ML", # for estimation use REML
                      test = "t",
                      data = data_p,
                      sparse = TRUE)
```

```{r}
load(here("RData", "full_model1.RData"))
summary(full_model1)
r2_ml(full_model1, data_p)
```
```{r}
load(here("RData", "full_model1.RData"))
summary(full_model1)
r2_ml(full_model1, data_p)
mod1 <- orchaRd::mod_results(full_model1, 
                    group = "study_ID", 
                    mod = "functional_group",
                    weights = "prop"
                    )
orchard_plot(mod1,
             mod = "functional_group", 
             group = "study_ID", 
             xlab = "lnRR", 
             angle = 45,
             trunk.size = 0.5)
```

# Model selection

```{r}
load(here("RData", "best_model1.RData"))
subset(mod.candidate, delta <= 4, recalc.weights = FALSE)
sw(mod.candidate)
```

```{r}
weights <- read_csv(here("Data", "sum_of_weights_AIC_fullmodel1.csv")) #upload data from sw(mod.candidate)

weights <- weights %>% 
  mutate(weights_percentage = round( Sum_of_weights * 100))

weights$Predictor <- factor(weights$Predictor, levels = weights$Predictor[order(weights$weights_percentage, weights$R2_marginal)])


AIC_weights <- ggplot(weights, aes(Predictor, Sum_of_weights)) +
  geom_col(aes(fill = ""), width = 0.7) +
  geom_text(aes(label = paste0(weights_percentage, "%"), x = Predictor), 
            position = position_stack(vjust = 0.5), 
            size = 4.5) +
  geom_text(aes(label = paste("R2 =", sprintf("%.3f", R2_marginal)), x = Predictor, y =  max(Sum_of_weights)), #R2 conditional 
            position = position_stack(vjust = 1.07), 
            size = 4.5, color = "red") +
  theme_light() +
  coord_flip() +
  scale_fill_manual(values = c("#999999")) +
  scale_x_discrete(name = "Predictor") +
  scale_y_continuous(name = "AIC weights",
                     breaks = seq(0, 1, by = 0.2)) +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18),
        axis.text = element_text(size = 16),
        panel.grid.major = element_line(color = "grey", 
                                       linewidth  = 0.2, 
                                       linetype = "dashed"),
       panel.grid.minor = element_line(color = "grey", 
                                      linewidth  = 0.2, 
                                      linetype = "dotted"))
AIC_weights
```

# Publication bias

## Model 16: Small study effect bias

```{r, eval=FALSE}
MLMR_mod_ess.se <- rma.mv(yi = lnRR, 
                               V = VCV_lnRR, 
                               mods = ~ ess.se, # add adjusted based sampling error - tilde square root n as a moderator to test small study effect (see section "lnRR and variance calculations).
                               random = list(~1|study_ID,
                                          ~1|pfas_ID, 
                                          ~1|es_ID
                                          ), 
                               method = "REML", 
                               test = "t", 
                               data = dat
                               )
```

```{r}
load(here("RData", "MLMR_mod_ess.se.RData"))
summary(MLMR_mod_ess.se)
```

## Model 17: Time-lag bias

```{r, eval = FALSE}
MLMR_mod_year.c <- metafor::rma.mv(lnRR,
                            VCV_lnRR,
                            mods = ~ scale(year_publication),
                            random = list(~1|study_ID,
                                          ~1|pfas_ID, 
                                          ~1|es_ID
                                          ),
                            data = dat)
```

```{r}
load(here("RData", "MLMR_mod_year.c.RData"))
summary(MLMR_mod_year.c)
```

```{r}
pb_bubble <- orchaRd::mod_results(MLMR_mod_year.c,
                                  mod = "year_publication",
                                  group = "study_ID",
                                  data = dat)

orchaRd::bubble_plot(pb_bubble,
                     group = "study_ID",
                     mod = "year_publication",
                     xlab = "Publication year", 
                     ylab = "Mean ratio (lnRR)",
            legend.pos = "bottom.right",
            k.pos = "top.right",
            ci.col = "red",
            pi.col = "black",
            est.col = "black") +
  ggtitle("c)") +
  theme(plot.title = element_text(size = 18),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 14)) +
  xlab("Year") +
  ylab("lnRR")
```

# Sensitivity analyses

## Model 18: Leave-one-out-analyses

```{r}
dat <- dat %>%
  mutate(leave_out = study_ID)

dat$leave_out <- as.factor(dat$leave_out)


LeaveOneOut_effectsize <- list()
for (i in 1:length(levels(dat$leave_out))) {
  temp_dat <- dat %>%
    filter(leave_out != levels(dat$leave_out)[i])
  
  VCV_leaveout <- vcalc(vi = temp_dat$var_lnRR, cluster = temp_dat$measurement_ID_A, rho = 0.5)
  
  LeaveOneOut_effectsize[[i]] <-  rma.mv(yi = lnRR,
                                         V = VCV_leaveout, 
                                         random = list(~1|study_ID,
                                                       ~1|pfas_ID,
                                                       ~1|es_ID),
                                         test = "t",
                                         sparse = TRUE,
                                         data = temp_dat[temp_dat$leave_out != levels(temp_dat$leave_out)[i], ])
}

# writing function for extracting est, ci.lb, and ci.ub from all models
est.func <- function(model) {
  df <- data.frame(est = model$b, lower = model$ci.lb, upper = model$ci.ub)
  return(df)
}

# using dplyr to form data frame
MA_oneout <- lapply(LeaveOneOut_effectsize,function(x) est.func(x)) %>%
  bind_rows %>%
  mutate(left_out = levels(dat$leave_out))


# telling ggplot to stop reordering factors
MA_oneout$left_out <- as.factor(MA_oneout$left_out)
MA_oneout$left_out <- factor(MA_oneout$left_out, levels = MA_oneout$left_out)

# saving the runs
saveRDS(MA_oneout, here("Rdata", "MA_oneout.RDS"))
```

```{r}
MA_oneout <- readRDS(here("Rdata", "MA_oneout.RDS"))

# plotting
leaveoneout <- ggplot(MA_oneout) + geom_hline(yintercept = 0, lty = 2, lwd = 1) +

  geom_hline(yintercept = ma_model$ci.lb, lty = 3, lwd = 0.75, colour = "black") +
  geom_hline(yintercept = ma_model$b, lty = 1, lwd = 0.75, colour = "black") + 
  geom_hline(yintercept = ma_model$ci.ub,
             lty = 3, lwd = 0.75, colour = "black") + 
  geom_pointrange(aes(x = left_out, y = est,
                      ymin = lower, ymax = upper)) + 
  xlab("Study left out") + 
  ylab("lnRR (effect size), 95% CI") +
  coord_flip() + 
  theme(panel.grid.minor = element_blank()) + theme_bw() + theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor.x = element_blank()) + theme(axis.text.y = element_text(size = 6))

leaveoneout
```

## Model 19: Adult female concentrations and same nest data only

```{r, eval=FALSE}
dat2_sa_model <- rma.mv(yi = lnRR,
             V = VCV_lnRR_dat2, 
             random = list(~1|study_ID,
                            ~1|pfas_ID,
                            ~1|es_ID
                           ),
             test = "t",
             data = dat2_sa)
dat2_sa_model <- robust(dat2_sa_model, dat2_sa$measurement_ID_P)
```

```{r}
load(here("RData", "dat2_sa_model.RData"))
summary(dat2_sa_model)
```

```{r}
I2 <- orchaRd::i2_ml(dat2_sa_model)
orchaRd::orchard_plot(dat2_sa_model,
             mod = "1",
             group = "study_ID", 
             xlab = "lnRR",
             alpha = 0.6,
             trunk.size = 3,
             branch.size = 1.5,
             twig.size = 1,
             k.pos = "right",
             colour = TRUE,
             fill = FALSE) +  
  annotate(geom = "text",
           x = 1.2,
           y = 6.2, 
           label = paste0("italic(I)^{2} == ", round(I2[1],4)),
           color ="black",
           parse = TRUE, 
           size = 3.5) +
           #scale_colour_manual(values = "darkorange")+ # change colours
           #scale_fill_manual(values="darkorange")+ 
           scale_size_continuous(range = c(1, 7)) + # change point scaling
  ggtitle("") +
  theme(panel.border = element_rect(colour = "black", 
                                             fill=NA,
                                             size=1.3), # border around the plot
                 text = element_text(size = 15), # change font sizes
                 legend.title = element_text(size = 12),
                 legend.text = element_text(size = 10))
```

## Model 20: Limit of detection/quantification treatment strategy

```{r}
load(here("RData", "ma_model2.RData"))
ma_model2 <- robust(ma_model2, dat$measurement_ID_P)
summary(ma_model2)
```

```{r}
I2 <- orchaRd::i2_ml(ma_model2)

orchaRd::orchard_plot(ma_model2,
             mod = "1",
             group = "study_ID", 
             xlab = "lnRR",
             alpha = 0.6,
             trunk.size = 3,
             branch.size = 1.5,
             twig.size = 1,
             k.pos = "right",
             colour = TRUE,
             fill = FALSE) +  
  annotate(geom = "text",
           x = 1.2,
           y = 6.2, 
           label = paste0("italic(I)^{2} == ", round(I2[1],4)),
           color ="black",
           parse = TRUE, 
           size = 3.5) +
           #scale_colour_manual(values = "darkorange")+ # change colours
           #scale_fill_manual(values="darkorange")+ 
           scale_size_continuous(range = c(1, 7)) + # change point scaling
  ggtitle("") +
  theme(panel.border = element_rect(colour = "black", 
                                             fill=NA,
                                             size=1.3), # border around the plot
                 text = element_text(size = 15), # change font sizes
                 legend.title = element_text(size = 12),
                 legend.text = element_text(size = 10))
```

## Model 21: Dataset without SD values imputation

```{r, eval=FALSE}
data_sa <- escalc(measure = "ROM",
                  m1i = mean_P,
                  m2i = mean_A, 
                  sd1i = sd_P, 
                  sd2i = sd_A, 
                  n1i = n_P,
                  n2i = n_A, 
                  data = dat %>% filter(sd_A > 0))

VCV_sa <- impute_covariance_matrix(data_sa$vi,
                                     cluster = data_sa$measurement_ID_A, 
                                     r = 0.5)

ma_model_sa <- rma.mv(yi = yi,
             V = VCV_sa, 
             random = list(~1|study_ID,
                           #~1|pfas_ID,
                           ~1|es_ID
              ),
             test = "t",
             data = data_sa)
ma_model_sa <- robust(ma_model_sa, data_sa$measurement_ID_P)
```

```{r}
load(here("RData", "ma_model_sa.RData"))
summary(ma_model_sa)
```

```{r}
I2 <- orchaRd::i2_ml(ma_model_sa)
orchaRd::orchard_plot(ma_model_sa,
             mod = "1",
             group = "study_ID", 
             xlab = "lnRR",
             alpha = 0.6,
             trunk.size = 3,
             branch.size = 1.5,
             twig.size = 1,
             k.pos = "right",
             colour = TRUE,
             fill = FALSE) + 
  annotate(geom = "text",
           x = 1.2,
           y = 6.2, 
           label = paste0("italic(I)^{2} == ", round(I2[1],4)),
           color ="black",
           parse = TRUE, 
           size = 3.5) +
           #scale_colour_manual(values = "darkorange")+ # change colours
           #scale_fill_manual(values="darkorange")+ 
           scale_size_continuous(range = c(1, 7)) + # change point scaling
  theme(panel.border = element_rect(colour = "black", 
                                             fill=NA,
                                             size=1.3), # border around the plot
                 text = element_text(size = 15), # change font sizes
                 legend.title = element_text(size = 12),
                 legend.text = element_text(size = 10))
```
